### 2022-11-13 chapter1.tex
Moved some caption text into main text for realignment figure

The aligner MAFFT has a mode for addressing over-alignment with a parameter, \textit{a\textsubscript{max}}, that adjusts the strength of the correction~\cite{Katoh2013, Katoh2016}. \textit{a\textsubscript{max}} varies between 0 and 1, but at values above 0.8, the correction severely degrades the alignment of conserved regions. Thus, in our pipeline the sequences were aligned with a conservative value of 0.4. Though some cases of over-alignment remained, most conserved regions were reliably aligned with few to no errors. To correct the remaining errors in alignments of the single copy orthologs, a statistical model of each alignment called a profile HMM was constructed from the well-aligned columns~\cite{Eddy2009}. The original sequences were then aligned to these profiles. By defining highly conserved “anchor” regions, this approach largely prevents the alignment of chance sequence similarities in long poorly supported segments (Fig.~\ref{fig:realignment}). Furthermore, since profile HMMs explicitly model the beginnings and ends of alignments, they can fully exclude these segments from the termini.

\begin{figure}[h!]
\includegraphics[width=\textwidth]{realignment/out/merged.png}
\centering
\caption{\textbf{Alignment with long poorly supported segments.}
The alignments of representative sequences in orthologous groups 23D9 (A), 01E0 (B), and 07C3 (C) are shown before and after refinement. The refinement process removes long poorly supported segments at the termini. However, if residues are aligned to consensus columns before and after a long poorly segment, it remains in the alignment.}
\label{fig:realignment}
\end{figure}

>>>>

The aligner MAFFT has a mode for addressing over-alignment with a parameter, \textit{a\textsubscript{max}}, that adjusts the strength of the correction~\cite{Katoh2013, Katoh2016}. \textit{a\textsubscript{max}} varies between 0 and 1, but at values above 0.8, the correction severely degrades the alignment of conserved regions. Thus, in our pipeline the sequences were aligned with a conservative value of 0.4. Though some cases of over-alignment remained, most conserved regions were reliably aligned with few to no errors. To correct the remaining errors in alignments of the single copy orthologs, a statistical model of each alignment called a profile HMM was constructed from the well-aligned columns~\cite{Eddy2009}. The original sequences were then aligned to these profiles. By defining highly conserved “anchor” regions, this approach largely prevents the alignment of chance sequence similarities in long poorly supported segments. Furthermore, since profile HMMs explicitly model the beginnings and ends of alignments, they can fully exclude these segments from the termini. This effect is visible in the three examples shown in Figure \ref{fig:realignment}, where each has long poorly supported segments that are completely removed.

\begin{figure}[h!]
\includegraphics[width=\textwidth]{realignment/out/merged.png}
\centering
\caption{\textbf{Alignment with long poorly supported segments.}
The alignments of representative sequences in orthologous groups 23D9 (A), 01E0 (B), and 07C3 (C) are shown before and after refinement.}
\label{fig:realignment}
\end{figure}
